Increasing the topological gap by an order of magnitude through the geometry for Majorana SNS junctions.

### 2018-12-12 paper/snakemajoranas.tex
Rearanged and added to section VI(localization effects)

\comment{The gap is small because of long trajectories.}
One of the problems lying in the way of a stable system, is the appearance of a soft gap; the gap is greatly reduced for states with momentum directed along the length of the strip.
From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.

\comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
We show that introducing a zigzag or snake like geometry for the semiconductor removes these long trajectories and prevents the appearance of a soft gap.

@@

\comment{We consider a two-dimensional system with zigzag.}
We consider a system (Fig.~\ref{fig:setup}) consisting of a two dimensional strip of semiconductor, with superconductors adjacent on both sides.
As seen in the figure, we modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth snake like shape.
Just as the normal system[\cite{pientka2017topological}], a magnetic field pointed along the x direction is applied.
We model the system with a BdG Hamiltonian Eq.~\eqref{eq:hamiltonian}; the normal part has Rashba spin-orbit coupling and a Zeeman field, and apart from the kinetic term, the superconductors only have a superconducting term differ in superconducting phase.
For the zigzag geometry, we take a sawtooth like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.

@@

@@

\comment{We find the Majorana lengths by calculating the slowest decaying mode.}

@@

\comment{We also confirm that the specific shape does not matter.}

Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
We then superimpose them onto the geometry, as in figure \ref{fig:wavefunctions}.
For the ribbon system, we see that the Majorana coherence length is relatively large, not showing the decolalized nature sought after.
All of the zigzag type geometries however show greatly reduced coherence length.\tabularnewline
This can be explained by two effects: the increase in topological gap, but also the beforementioned reduction of the group velocity.

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
\caption{Wavefunctions for different sizes and geometries.
With (a) a straight system, (b) a zigzag system, (c) a system where the normal region is defined by two parallel sine waves, and (d) a system with the Laeven shape.
Inside the figure we indicate the Majorana length (or coherence length) $\xi$ and the topological energy gap $E_\textrm{gap}.$
We observe that $\xi$ for (a) is orders of magnitude longer and $E_\textrm{gap}$ orders of magnitude smaller than for (b, c, d), meaning that the details of the geometry do not matter.
\label{fig:wavefunctions}}
\end{figure}

@@

Additionally in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, the reflected part will eventually ``find'' a surface with which it is perpendicular to.

>>>>

\comment{The gap is small because of long trajectories.}
One of the biggest challenges in constructing stable Majoranas is the appearance of a soft gap; where the gap in the density of states is greatly reduced for states with momentum directed along the length of the strip.
From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
Additionally, these long trajectories have long flight times $\tau_f$ and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap.

\comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
In this paper we show that introducing a zigzag or snake like geometry for the semiconductor eliminates these long trajectories and prevents the appearance of a soft gap.

@@

\comment{We consider a two-dimensional system with zigzag.}
We consider a system (Fig.~\ref{fig:setup}) consisting of a two dimensional strip of semiconductor, with superconductors on both sides.
We modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth sinusoidal like shape.
Similar to the straight system \cite{pientka2017topological}, a magnetic field $B_x$ pointed along the $x$ direction is applied.
We model the system with a BdG Hamiltonian Eq.~\eqref{eq:hamiltonian}; the normal part has Rashba spin-orbit coupling and a Zeeman field, and apart from the kinetic term, the superconductors only have a superconducting term with a superconducting phase.
For the zigzag geometry, we take a sawtooth like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.

@@

\comment{The introduction of an SN interface at many angles also increases performance.}
Additionally in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, the reflected part will eventually ``find'' a surface with which it is perpendicular to. The transparency of the SN interface is thus improved for transversal modes.

@@

@@

\comment{We find the Majorana lengths by calculating the slowest decaying mode.}
Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
In figure \ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
For the ribbon system, we see that the Majorana coherence length is relatively large, not showing the decolalized nature sought after.
All of the zigzag type geometries however show greatly reduced coherence length.
This can be explained by two effects: the increase in topological gap, but also the before mentioned reduction of the group velocity.

\comment{We also confirm that the specific shape does not matter.}
Also note the similarity between the various shapes, sharp corners or more smoothlike, the effect is the same.

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
\caption{Wavefunctions for different sizes and geometries.
With (a) a straight system, (b) a zigzag system, (c) a system where the normal region is defined by lines parallel to a sinosoid, and (d) a system with vertically offset sinosoids.
Inside the figure we indicate the Majorana length (or coherence length) $\xi$ and the topological energy gap $E_\textrm{gap}.$
We observe that $\xi$ for (a) is orders of magnitude longer and $E_\textrm{gap}$ orders of magnitude smaller than for (b, c, d), meaning that the details of the geometry do not matter.
\label{fig:wavefunctions}}
\end{figure}

@@
